\documentclass[12pt]{article}

\usepackage[
    top=1.5cm,
    bottom=1.5cm,
    left=1.5cm,
    right=1.5cm,
    marginparwidth=0mm,
    marginparsep=0mm,
    headheight=15pt,
    centering,
    % showframe,
    % includefoot,
]{geometry}

\usepackage{tabularx}

\usepackage{titlesec}
\usepackage{anyfontsize}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage[super]{nth}

\usepackage[hidelinks]{hyperref}

% allows me to use inter is certain parts of the document
\usepackage{inter}

% ================== %
%   header formats
% ================== %
\titleformat{\section}
   {\intertabular\small\bfseries\MakeUppercase}{}{1em}{}
\titlespacing{\section}{-1pc}{*2}{*0.5}

\titleformat{\subsection}
   {\normalfont\normalsize\bfseries}{}{1em}{}
\titlespacing{\subsection}{-0.7pc}{*4}{*1.5}

\titleformat{\subsubsection}
   {\small\bfseries\sc}{}{1em}{}
\titlespacing{\subsection}{-0.5pc}{*4}{*1.5}



% Method 1: Using \linespread
%\linespread{0.9} % Adjust the value to your desired line spacing

% Method 2: Adjusting \baselineskip
%\setlength{\baselineskip}{0.9\baselineskip} % Adjust the value to your desired line spacing

\setlength{\parskip}{0pt} % Adjust the value to your desired line break height

\setitemize[0]{leftmargin=15pt}


% ========================== %
%   Format a project title
% ========================== %
\newcommand{\bigtitle}[5]{
  {\bf \large #1} \textemdash{} {\large \it #2} \hfill {#3}

  {\small #4}

  \smallskip

  {#5} % description

  \medskip
}

\newcommand{\medtitle}[3]{
  \textbf{\textit{#1}} \hfill {#2}

  \smallskip

  {#3} % content

  \medskip
}

\newcommand{\smalltitle}[2]{
   \textbf{\textit{#1}} #2

   \smallskip
}

\newcommand{\link}[2]{
   \underline{{\href{#1}{#2}}}
}

\newcommand{\course}[2]{
  {\small {\textbf{\textit{#1}}} {#2}}
}

% remove page numbering
\pagenumbering{gobble}

% remove all paragraph indents
\setlength{\parindent}{0pt}

% COLUMNS
\newcolumntype{L}{>{\hsize=0.6\hsize}X}
\newcolumntype{S}{>{\hsize=0.4\hsize}X}

\begin{document}
    {\fontsize{40}{50} \selectfont \bf \intertabular Gaetan Almela}

    \smallskip

    {\bf My name is Gaetan}. I am 22 years old and passionate for writing good
    code, and solving meaningful problems. I'm looking for a job in Software
    Engineering in the finance industry.

    \begin{center}
      \begin{multicols}{3}
       {\bf almela.io}

       gaetan@{\bf almela.io}

       github.com/{\bf llGaetanll}
      \end{multicols}
    \end{center}

    \section{Work Experience}

    \smallskip

    \bigtitle{SIG}{Large scale trading software}
    {
      \textit{Philadelphia} $\big|$ \textbf{Jun 2023 -- Aug 2023}
    }
    {}
    {
      \begin{itemize}
        \item[$-$] Implemented a data syncing system for software {\bf used by
          hundreds of traders every day}.
        \item[$-$] Developed and deployed a remote REST API to keep track of data
          relations between independent instances of the trading system, all in
          \texttt{C\#}.
        \item[$-$] Learned invaluable lessons working with larger teams,
          code bases, and shipping software that scales.
      \end{itemize}
    }

    \bigtitle{Arandis}{Data science in finance}
    {
      \textit{France} $\big|$ \textbf{Mar 2021 -- Apr 2021}
    }
    {}
    {
      \begin{itemize}
        \item[$-$] Developed over {\bf 60 fully automated} Selenium web scrapers to extract
              ETF fund data every day.
        \item[$-$] Performed data analysis in Numpy and Pandas on {\bf over
              45,000 data points} from hundreds of different sources.
        \item[$-$] Learned how to work in a team of other developers.
      \end{itemize}
    }

    \bigtitle{Amazon Marketplace}{Scraping the web}
    {
      \textit{France} $\big|$ \textbf{Jan 2019 -- Mar 2019}
    }
    {}
    {
      \begin{itemize}
        \item[$-$] Developed a fully automated scraper to extract {\bf over 30,000
              data points} from competitors.
        \item[$-$] Learned valuable lessons in structuring and writing larger programs.
      \end{itemize}
    }

    \section{Projects}

    \bigtitle{Wave Function Collapse}{Safety meets performance}
    {
      \link{https://github.com/llGaetanll/wfc}{GitHub}
      $\Big|$
      \textbf{2023}
    }
    {
      Implemented the Wave Function Collapse algorithm in Rust with compile
      time type checking, parallel processing, and arbitrary dimensional
      space and input type.
    }

    \bigtitle{obx}{Object manipulation done right}
    {
      \link{https://github.com/llGaetanll/obx/}{GitHub}
      /
      \link{https://www.npmjs.com/package/@almela/obx}{npm}
      $\Big|$
      \textbf{2022}
    }
    {
      obx is a fast, tiny, well documented, and battle-tested object
      manipulation library for JavaScript with over {\bf 1000 tests}. It is used
      in many of my projects including some listed below.
    }

    % \bigtitle{Klue}{Remembering the Kanji}
    % {
    %   \link{https://github.com/llGaetanll/Klue}{GitHub}
    %   /
    %   \link{https://klue.vercel.app/}{Website}
    %   $\Big|$
    %   \textbf{2019 -- 2022}
    % }
    % {
    %   Klue is a flashcard website designed to help you remember the Kanji
    %   using spaced repetition and by giving you statistics on your learning.
    %   Built using NextJs and Redux.
    % }

    \bigtitle{Accents}{Accent support for Chrome}
    {
      \link{https://github.com/eugli/Accents}{GitHub}
      /
      \link{https://chrome.google.com/webstore/detail/accents-spanish-portugues/laiognlohmgkmlfchcclnjnafgeinnpg}{Web Store}
      $\Big|$
      \textbf{2019}
    }
    {
      Co-founder of Accents, an extension for Chrome that adds easy accents
      to the keyboard. It emulates the accent system of \nobreak MacOS while adding
      keyboard shortcuts and functionalities. At its peak, the extension had
      over {\bf 40,000 users}.
    }

    \section{Education}

    \medtitle{University of Maryland}
    {\textbf{Fall 2019 -- Spring 2024}}
    {
       Computer Science and Mathematics Double Major. Expected to graduate May
       $\nth{20}$ 2024.
    }

    \course{CMSC320}{Data Science}, \course{CMSC420}{Data Structures},
    \course{CMSC422}{Machine Learning}, \course{CMSC424}{Database Design},
    \course{CMSC451}{Advanced Algorithms}, \course{STAT410}{Probability Theory}

    \section{Skills}

    \smalltitle{Web}{
      React, Redux, GraphQL, MongoDB, PostgreSQL, Actix Web
    }

    \smalltitle{Data Science}{
      Numpy, Pandas, SciKit Learn, SciPy, Jupyter
    }

    \smalltitle{Programming Languages}{
      Rust, JavaScript, Go, Python, Shell
    }

    \smalltitle{Other}{
      Efficient with {\bf GNU/Linux}, Fluent in {\bf English} and {\bf French},
      Rubik's Cube World Championship 2017 Contestant.
    }
\end{document}
